### 2018-08-02 acks.tex
Conclusion and discussion section finished

The authors contributed to this work as described below.  Andrei Rykhlevskii 
conceived and designed the simulations, wrote the paper, prepared figures 
and/or tables, performed the computation work, contributed to the software 
product, and reviewed drafts of the paper. Mr. Rykhlevskii is supported by the 
Department of Nuclear, Plasma, and Radiological Engineering.

>>>>

The authors contributed to this work as described below.  Andrei Rykhlevskii 
conceived and designed the simulations, wrote the paper, prepared figures 
and/or tables, performed the computation work, contributed to the software 
product, and reviewed drafts of the paper. Jin Whan Bae conceived and designed 
the simulations, wrote the paper, contributed to the software 
product, and reviewed drafts of the paper. Andrei Rykhlevskii and Jin Whan Bae 
is supported by the Department of Nuclear, Plasma, and Radiological Engineering.

### 2018-08-02 graph-abs/graph-abs.tex
Conclusion and discussion section finished

\newcommand{\Cyclus}{\textsc{Cyclus}\xspace}%
\newcommand{\Cycamore}{\textsc{Cycamore}\xspace}%
\graphicspath{ {images/} }

@@

\begin{document}
\begin{frontmatter}
\title{Graphical Abstract\\
Modeling and Simulation of Online Reprocessing in the Thorium-Fuelled Molten Salt Breeder Reactor}
\date{}                     %% if you don't need date to appear

@@

\begin{figure}[htbp!]
    \begin{center}
        \includegraphics[width=\textwidth]{./highlight.png}
    \end{center}
    \caption{A very fancy image important to the paper.}
    \label{fig:graph-abs}
\end{figure}

>>>>

%\newcommand{\Cyclus}{\textsc{Cyclus}\xspace}%
%\newcommand{\Cycamore}{\textsc{Cycamore}\xspace}%
\graphicspath{ {../figures/} }

@@

\begin{document}
\begin{frontmatter}
\title{Graphical Abstract\\
Modeling and Simulation of Online Reprocessing in the Thorium-Fueled Molten Salt Breeder Reactor}
\date{}                     %% if you don't need date to appear

@@

\begin{figure}[htbp!]
    \begin{center}
        \includegraphics[width=\textwidth]{view_serpent.png}
    \end{center}
    \caption{Plan and elevation views of SERPENT 2 Molten Salt Breeder Reactor model developed in this work.}
    \label{fig:graph-abs}
\end{figure}
\begin{figure}[htbp!]
    \begin{center}
        \includegraphics[width=\textwidth]{ser_zone_II.png}
    \end{center}
    \caption{Detailed view of Molten Salt Breeder Reactor zone II model.}
    \label{fig:serpent-zoneII}
\end{figure}
\begin{figure}[htbp!]
    \begin{center}
        \includegraphics[width=\textwidth]{zone_I_element_ref.png}
    \end{center}
    \caption{Graphite moderator elements for zone I.}
  	\label{fig:I_element_ref}
\end{figure}
\begin{figure}[htbp!]
    \begin{center}
		\includegraphics[width=\textwidth]{zone_II_element_ref.png}
    \end{center}
	\caption{Graphite moderator elements for zone II-A.}
	\label{fig:II_element_ref}
\end{figure}
\begin{figure}[htbp!]
    \begin{center}
		\includegraphics[width=\textwidth]{periodic_map.png}
    \end{center}
	\caption{Processing options for Molten Salt Reactor fuels.}
	\label{fig:periodic_tab}
\end{figure}
\begin{figure}[htbp!]
    \begin{center}
		\includegraphics[width=0.75\textwidth]{saltproc_flowchart.pdf}
    \end{center}
  \caption{Flow chart for the Saltproc python-based tools.}
  \label{fig:saltproc_flow}
\end{figure}
\begin{figure}[htbp!]
    \begin{center}
		\includegraphics[width=\textwidth]{keff.png}
    \end{center}
	\caption{Effective multiplication factor dynamics for full-core model for a 60-year reactor operation. The confidence interval $\sigma=\pm15pcm$ is shaded.}
	\label{fig:keff}
\end{figure}
\begin{figure}[htbp!]
    \begin{center}
		\includegraphics[width=\textwidth]{major_isotopes_adens.png}
    \end{center}
	\caption{Number density of major nuclides during 60 years of reactor operation.}
	\label{fig:adens_eq}
\end{figure}
\begin{figure}[htbp!]
    \begin{center}
		\includegraphics[width=\textwidth]{fissile_short.png}
    \end{center}
	\caption{Number density of fissile in epithermal spectrum nuclides accumulation during the reactor operation.}
	\label{fig:fissile_short}
\end{figure}
\begin{figure}[htbp!]
    \begin{center}
		\includegraphics[width=\textwidth]{spectrum.png} 
    \end{center}
	\caption{Neutron flux energy spectrum normalized by unit lethargy for initial and equilibrium fuel salt composition.}
	\label{fig:spectrum}
\end{figure}
\begin{figure}[htbp!]
    \begin{center}
		\includegraphics[width=\textwidth]{spectrum_zones.png} 
    \end{center}
	\caption{Neutron flux energy spectrum in different core regions normalized by unit lethargy for the initial and equilibrium fuel salt composition.}
	\label{fig:spectrum_zones}
\end{figure}
\begin{figure}[htbp!]
    \begin{center}
		\includegraphics[width=\textwidth]{radial_flux.png} 
    \end{center}
	\caption{Radial neutron flux distribution for initial and equilibrium fuel salt composition.}
	\label{fig:radial_flux}
\end{figure}
\begin{figure}[htbp!]
    \begin{center}
		\includegraphics[width=\textwidth]{power_distribution_eq.png} 
    \end{center}
	\caption{Normalized power density for both initial and equilibrium fuel salt composition.}
	\label{fig:pow_den}
\end{figure}
\begin{figure}[htbp!]
    \begin{center}
		\includegraphics[width=\textwidth]{breeding_distribution_eq.png} 
    \end{center}
	\caption{$^{232}$Th neutron capture reaction rate normalized by total flux for both initial and equilibrium fuel salt composition.}
	\label{fig:breeding_den}
\end{figure}
\begin{figure}[htbp!]
    \begin{center}
		\includegraphics[width=\textwidth]{Th_refill_rate.png} 
    \end{center}
	\caption{$^{232}$Th feed rate over 60 years of Molten Salt Breeder Reactor operation.}
	\label{fig:th-rate}
\end{figure}
\begin{figure}[htbp!]
    \begin{center}
		\includegraphics[width=\textwidth]{keff_rem_cases.png} 
    \end{center}
	\caption{Calculated effective multiplication factor for full-core model with removal of different fission product groups over 10 years of operation. The confidence interval $\pm\sigma$ is shaded.}
	\label{fig:fp-removal}
\end{figure}

### 2018-08-02 highlights/highlights.tex

\begin{document}
\begin{frontmatter}
\title{Modeling and Simulation of Online Reprocessing in the Thorium-Fuelled Molten Salt Breeder Reactor}
\end{frontmatter}
\section*{Highlights}
\begin{itemize}
       \item Highlight 1
       \item Highlight 2
       \item Highlight 3
\end{itemize}
\end{document}

>>>>

\begin{document}
\begin{frontmatter}
\title{Modeling and Simulation of Online Reprocessing in the Thorium-Fueled Molten Salt Breeder Reactor}
\end{frontmatter}
\section*{Highlights}
\begin{itemize}
       \item Python script, SaltProc, and SERPENT are used to simulate material feeds and removals during depletion in MSBR.
       \item Analysis of the startup of a thorium-fueled MSBR to find equilibrium fuel composition.
       \item Effects of the fuel salt irradiation with online reprocessing on MSBR operations.
       \item Fission products online removal benefits for thermal spectrum MSBR.
\end{itemize}
\end{document}

### 2018-08-02 methods.tex
Results finished

Figure~\ref{fig:serpent_plan_view} demonstrate the configuration of the \gls{MSBR} vessel, core configuration, ``fission" (zone I) and ``breeding" (zone II) regions inside the vessel. The core has two radial zones bounded by a solid cylindrical graphite reflector and the vessel wall. The central zone, zone I, in which 13\% of the volume is fuel salt and 87\% graphite. Zone I composed of 1,320 graphite cells, 2 graphite control rods, and 2 safety\footnote{These rods needed for emergency shutdown only.} rods. The under-moderated zone, zone II, with 37\% fuel salt, and radial reflector, surrounds the zone I core region and serves to diminish neutron leakage. Zones I and II are surrounded radially and axially by fuel salt (figure~\ref{fig:serpent_zoneII}). This space for fuel is necessary for injection and flow of molten salt.

@@

These graphite elements have a mostly rectangular shape with lengthwise ridges at each corner that leave space for salt flow elements. Various element sizes reduce the peak damage flux and power density in the center of the core to prevent local graphite damage. Zone I is well-moderated to achieve the desired fission power density. Figure~\ref{fig:I_element_ref} demonstrates the elevation and plan views of graphite elements of zone I \cite{robertson_conceptual_1971} and their SERPENT model \cite{rykhlevskii_full-core_2017}.

\begin{figure}[ht!] % replace 't' with 'b' to 
  \centering
  \includegraphics[width=\textwidth]{zone_I_element_ref.png}
  \caption{Graphite moderator elements for zone I \cite{robertson_conceptual_1971,rykhlevskii_full-core_2017}.}
  \label{fig:I_element_ref}
\end{figure}

@@

Figure~\ref{fig:saltproc_flow} illustrates the  online reprocessing simulation algorithm the 
coupled SaltProc and SERPENT 2. To perform a depletion step,
SaltProc reads an external SERPENT 2 template file which is defined by the user. This file 
contains input cards with parameters such as geometry,
moderator and construction materials isotopic composition, neutron population, criticality 
cycles, total heating power, and boundary conditions.
After the depletion calculation, SaltProc reads the depleted fuel composition file (\texttt{
.bumat1}) and stores the depleted
composition isotopic vector in an HDF5 database. SaltProc only stores and edits the isotopic 
composition of the fuel stream,
which makes SaltProc a flexible tool to model any geometry: an infinite medium, a unit cell, a 
multi-zone simplified assembly, or a full core.
This flexibiliity allows the user to perform simulations of varying fidelity and computational 
intensity.

\begin{figure}[htp!] % replace 't' with 'b' to 
  \centering
  \includegraphics[width=0.75\textwidth]{saltproc_flowchart.pdf}
  \caption{Flow chart for the Saltproc python-based tools.}
  \label{fig:saltproc_flow}
\end{figure}

SaltProc can manage as many material streams as desired. It also may work with multiple depletion 
materials. At the end of a each depletion
step, SaltProc reads the depleted compositions and tracks each material stream individually. 
Following this, it applies chemical
separation functions to fuel stream vectors. These vectors then form a matrix (isotopics x 
timesteps) which SaltProc stores in an HDF5 database
and prints into the SERPENT 2 composition file for the next depletion calculation.

>>>>

Figure~\ref{fig:serpent_plan_view} demonstrate the configuration of the \gls{MSBR} vessel, core configuration, ``fission" (zone I) and ``breeding" (zone II) regions inside the vessel. The core has two radial zones bounded by a solid cylindrical graphite reflector and the vessel wall. The central zone, zone I, in which 13\% of the volume is fuel salt and 87\% graphite. Zone I composed of 1,320 graphite cells, 2 graphite control rods, and 2 safety\footnote{ These rods needed for emergency shutdown only.} rods. The under-moderated zone, zone II, with 37\% fuel salt, and radial reflector, surrounds the zone I core region and serves to diminish neutron leakage. Zones I and II are surrounded radially and axially by fuel salt (figure~\ref{fig:serpent_zoneII}). This space for fuel is necessary for injection and flow of molten salt.

@@

These graphite elements have a mostly rectangular shape with lengthwise ridges at each corner that leave space for salt flow elements. Various element sizes reduce the peak damage flux and power density in the center of the core to prevent local graphite damage. Zone I is well-moderated to achieve the desired fission power density. Figure~\ref{fig:I_element_ref} demonstrates the elevation and plan views of graphite elements of zone I \cite{robertson_conceptual_1971} and their SERPENT model \cite{rykhlevskii_full-core_2017}.
\begin{figure}[ht!] % replace 't' with 'b' to 
  \centering
  \includegraphics[width=\textwidth]{zone_I_element_ref.png}
  \caption{Graphite moderator elements for zone I \cite{robertson_conceptual_1971,rykhlevskii_full-core_2017}.}
  \label{fig:I_element_ref}
\end{figure}

@@

Figure~\ref{fig:saltproc_flow} illustrates the  online reprocessing simulation algorithm the 
coupled SaltProc and SERPENT 2. To perform a depletion step,
SaltProc reads an external SERPENT 2 template file which is defined by the user. This file 
contains input cards with parameters such as geometry,
moderator and construction materials isotopic composition, neutron population, criticality 
cycles, total heating power, and boundary conditions.
After the depletion calculation, SaltProc reads the depleted fuel composition file (\texttt{
.bumat1}) and stores the depleted
composition isotopic vector in an HDF5 database. SaltProc only stores and edits the isotopic 
composition of the fuel stream,
which makes SaltProc a flexible tool to model any geometry: an infinite medium, a unit cell, a 
multi-zone simplified assembly, or a full core.
This flexibiliity allows the user to perform simulations of varying fidelity and computational 
intensity.
\begin{figure}[ht!] % replace 't' with 'b' to 
  \centering
  \includegraphics[width=0.75\textwidth]{saltproc_flowchart.pdf}
  \caption{Flow chart for the Saltproc python-based tools.}
  \label{fig:saltproc_flow}
\end{figure}
SaltProc can manage as many material streams as desired. It also may work with multiple depletion 
materials. At the end of a each depletion step, SaltProc reads the depleted compositions and tracks each material stream individually. Following this, it applies chemical separation functions to fuel stream vectors. These vectors then form a matrix (isotopics x timesteps) which SaltProc stores in an HDF5 database and prints into the SERPENT 2 composition file for the next depletion calculation.
